\bf Forecast Reconciliation: A geometric view with new insights on bias correction.

### 2019-09-02 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex

	Consider the Euclidean distance between a forecast and the target. This is equivalent to the root of the sum of squared forecast errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}

		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2\ge 0$ this implies,
		\begin{equation}
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2\ge\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
		\end{equation}
		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}$.  Taking the square root of both sides proves the desired result.
	\end{proof}

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}\label{fig:Schematic_OLSRecon}

	\end{figure}

@@

Thinking of the problem in terms of a geometry defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$ is also quite instructive when it comes to thinking about the connection between distances and loss functions. In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.  For diagonal $\bm{W}^{-1}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised as follows:

	\begin{theo}[General distance reducing property]\label{th:gdistred}
        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ then:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}.
		\end{equation}
	\end{theo}
	\begin{proof}
    The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
    \end{proof}

@@

	\todo{Rob can you please read to make sure you are happy with this.}Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.  This will be demonstrated using a real data set in the empirical study in section~\ref{sec:comparebase}.

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection shown in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts an oblique projection along $\bm{R}$ for all the gray points, yielding reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

%	\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\input{Figs/insampledir}
%		}
%		\caption{A schematic to represent MinT reconciliation. Points in orange colour represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace. $\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
%	\end{figure}
%		
%	\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\input{Figs/oblique_justification2}
%		}
%		\caption{A schematic to represent MinT reconciliation. Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
%	\end{figure}
%	
%	\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\includegraphics{Figs/OrthProj.pdf}}
%		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$. Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
%	\end{figure}
%	
%	
%	\begin{figure}[H]
%	\centering
%	%\vspace{-0.9cm}
%	\small
%	\resizebox{\linewidth}{!}{
%		\includegraphics{Figs/ObliqueProjection.pdf}}
%	\caption{All gray points are obliquely projected along the direction of $\bm{R}$. Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
%	\end{figure}

%	\begin{figure}
%		\centering
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf}
%%			\label{fig:InsampDir_1}
%		\end{subfigure}
%		\hfill
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf}
%%			\label{fig:InsampDir_2}
%		\end{subfigure}
%		
%		\vspace{1cm}
%		
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf}
%%			\label{fig:OrthProj}
%		\end{subfigure}
%		\hfill
%		\begin{subfigure}[t]{0.45\textwidth}
%			\centering
%			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf}
%%			\label{fig:ObliqProj}
%		\end{subfigure}
%		
%%		\begin{subfigure}[t]{\textwidth}
%%			\centering
%%			\includegraphics[width=\linewidth]{example-image-c.pdf}
%%			\caption{Price regulation} \label{fig:timing3}
%%		\end{subfigure}
%		\caption{A schematic to represent orthogonal and oblique reconciliation.  Points in orange colour in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
%	\end{figure}
%
%	\begin{figure}
%	
%	\begin{adjustbox}{minipage=\linewidth,scale=0.7}
%	\begin{subfigure}[t]{0.45\textwidth}
%%		\centering
%		\input{Figs/InsampDir_1}
%		%			\label{fig:InsampDir_1}
%	\end{subfigure}
%	\hspace{1cm}
%	\begin{subfigure}[t]{0.45\textwidth}
%%		\centering
%		\input{Figs/InsampDir_2}
%		%			\label{fig:InsampDir_2}
%	\end{subfigure}
%	
%	\vfill
%%	\vspace{0.3cm}
%	
%	\begin{subfigure}[t]{0.45\textwidth}
%%		\centering
%		\input{Figs/Orthproj}
%		%			\label{fig:OrthProj}
%	\end{subfigure}
%	\hspace{1cm}
%	\begin{subfigure}[t]{0.45\textwidth}
%%		\centering
%		\input{Figs/ObliqProj}
%		%			\label{fig:ObliqProj}
%	\end{subfigure}
%	
%	%		\begin{subfigure}[t]{\textwidth}
%	%			\centering
%	%			\includegraphics[width=\linewidth]{example-image-c.pdf}
%	%			\caption{Price regulation} \label{fig:timing3}
%	%		\end{subfigure}
%	
%	\end{adjustbox}
%\caption{A schematic to represent orthogonal and oblique reconciliation.  Orange colour points in top left figure represent the insample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
%\end{figure}

\begin{figure}[H]
    \centering
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
        \caption{}
    \end{subfigure}
    \caption{A schematic to represent orthogonal and oblique reconciliation.  Orange colour points in top left figure represent the insample errors.$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection. } \label{fig:OthogonalVSOblique_projection_new}
\end{figure}

%		\begin{figure}[H]
%		\centering
%		%\vspace{-0.9cm}
%		\small
%		\resizebox{\linewidth}{!}{
%			\input{Figs/ObliqueProjection}
%		}
%		\caption{\textcolor{red}{write caption}}\label{fig:Oblique_projection}
%	\end{figure}

%\begin{figure}
%	\centering
%	\begin{subfigure}{0.47\textwidth}
%		\resizebox{\linewidth}{!}{
%			\input{Figs/Orth.proj.tex}}
%		\caption{bla bla}
%	\end{subfigure}
%	\begin{subfigure}{0.47\textwidth}
%		\resizebox{\linewidth}{!}{
%			\input{Figs/ObliqueProjection.tex}}
%			\caption{bla bla}
%	\end{subfigure}
%\end{figure}

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/Schem_3D}
		}
		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$. If $s\circ g$ is a projection not onto $\mathfrak{s}$ but onto $\mathfrak{L}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bar{\bm{\mu}} \in \mathfrak{L}$.}\label{fig:Schematic_3D}
	\end{figure}

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix. However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.  This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.

@@

	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such it may be possible to use the same errors to bias correct.  Geometrically, the intuition is simple.  In top left panel in Figure \ref{fig:OthogonalVSOblique_projection_new}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.  Nonetheless there are also a number of pitfalls to such an approach.  First, for the very construction we consider, where bias is induced by taking a log or Box Cox transformation, bias should be corrected by a multiplicative rather than an additive factor.  Second, if in-sample errors are non-stationary due to model misspecification structural breaks then the proposes method for bias correction may break down.

@@

	%\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here. This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.} 
	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice. Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}). However, our motivation in this study is twofold.  First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts and in contrast to previous studies we consider individual periods rather than computing averages over a rolling window.  Second, we demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.

@@

	We use ``overnight trips'' across Australia as a measure of domestic tourism flows. The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. We disaggregate Tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers. Hence, there are $110$ series across the hierarchy with $75$ bottom-level series. More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix. The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.

Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the aggregate overnight trips for Australia. As is usual with tourism data, overnight these show a strong seasonal pattern. Overnight trips peak in January corresponding to the summer vacation season in Australia. There are also some lower peaks observed in April, July and October corresponding to school term breaks. On the other hand the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation. The time plot also shows a pronounced upward trend starting from around 2010 till the end of the sample, with flows being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.

The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the hierarchy. The panels below show some selected series from the second-level zones and the bottom-level regions of the geographical hierarchy. The plots display the diversity of time series features, within but also between levels. For example, noticeable at the first-level is the asynchronous seasonal pattern between Northern Territory and the other states. For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February. This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season. Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being noisier compared to the series from levels above. This of course highlights the importance of modelling series at all levels without any loss of valuable information. We should note here that we observed an anomalous (extremely high) observation for `Adelaide Hills' for December-2002. We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.

@@

    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling \todo{George please check} and MinT use a shrinkage estimator for ${\bm W}$.  Squared forecast errors are computed for each series and aggregated, i.e. we compute the loss function described in Section~\ref{sec:orthogonal}.  We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicat that reconciled forecasts are more accurate. The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window.  As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts, the entire boxplot for OLS reconciliation is above zero.  This is not the case for WLS and MinT which for some windows perform worse than base forecasts.  The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.  Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.\todo{Get correct results in for figure with boxplots}

    \begin{figure}[H]
    	\centering
    	\small
    	\includegraphics[width = \textwidth]{Figs/OrthVsOblq_Proj_Emp_results.pdf}
    	\caption{MSE difference between base forecasts and reconciled forecasts over the replications is presented for forecast horizons $h = 1,...,6$. Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
    \end{figure}

>>>>

	Consider the Euclidean distance between the target and a forecast. This is equivalent to the root of the sum of squared forecast errors over the entire hierarchy. Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$. The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
		\begin{equation}
		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
		\end{equation}

		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2\ge 0$ this implies,
		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2\ge\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
		\end{equation}
		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}$.  Taking the square root of both sides proves the desired result.
	\end{proof}

@@

	\begin{figure}[H]
		\centering \includegraphics[width=0.6\textwidth]{Figs/orth_pointforerec_schematic.pdf}
		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}\label{fig:Schematic_OLSRecon}
	\end{figure}

@@

Thinking of the problem in terms of a geometry defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$ is also quite instructive when it comes to thinking about the connection between distances and loss functions. In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\bm{y}-\hat{\bm{y}})'\bm{W}^{-1}(\bm{y}-\hat{\bm{y}})$.  For diagonal $\bm{W}^{-1}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised as follows:

	\begin{theo}[General distance reducing property]\label{th:gdistred}
        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ then:
		\begin{equation}
		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}.
		\end{equation}
	\end{theo}
	\begin{proof}
    The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
    \end{proof}

@@

	\todo{Rob can you please read to make sure you are happy with this.}Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.  This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.

@@

	Figure~\ref{fig:OthogonalVSOblique_projection} provides geometrical intuition into the MinT method.  Suppose that the orange points in panel (a) represent in-sample forecast errors.  These provide information on the most likely direction of large deviations from the coherent subspace $\mathfrak{s}$.  This direction is denoted by $\bm{R}$.  Panel (b) shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection. Panel (c) shows the orthogonal projection of every potential base forecast onto the coherent subspace. Panel (d) depicts an oblique projection along $\bm{R}$ for all the gray points. The oblique projection yields reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.

\begin{figure}[H]
    \centering
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
        \caption{}
    \end{subfigure}    \begin{subfigure}[!h]{0.48\textwidth}
        \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
        \caption{}
    \end{subfigure}
    \caption{A schematic representing orthogonal and oblique reconciliations.  The orange points in (a) represent in-sample errors. $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$. Grey points in (b) indicate  potential base forecasts while the blue dot ${\hat{\bm y}}$ represents one such realisation. The black dot ${\bm y}$ denotes the (unknown) target of the forecast. (c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.} \label{fig:OthogonalVSOblique_projection}
\end{figure}

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\input{Figs/Schem_3D}
		}
		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$. If a projection is onto $\mathfrak{L}$ instead of $\mathfrak{s}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bm{\mu}^* \in \mathfrak{L}$.}\label{fig:Schematic_3D}
	\end{figure}

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix. However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias. Dropping the constraint compromises all of the attractive properties of projections.  Opening the door to reconciliation methods that change already coherent base forecasts would seem to suggest an increase in the variability of the forecast.  This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.

@@

	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such it may be possible to use the same errors to bias correct.  Geometrically, the intuition is simple.  In panel (a) of Figure \ref{fig:OthogonalVSOblique_projection}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.  Nonetheless there are also a number of pitfalls to such an approach.  First, for the very construction we consider, where bias is induced by taking a log or Box Cox transformation, bias should be corrected by a multiplicative rather than an additive factor.  Second, if in-sample errors are non-stationary due to model misspecification or structural breaks, then the proposed method for bias correction may break down.

@@

	%\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here. This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.}
	Using an empirical application to forecast Australian domestic tourism flows, we illustrate the usefulness of projection based reconciliation in practice. Previous studies have found that reconciliation improves point forecast accuracy in domestic tourism flows for Australia \citep[see for example][]{Athanasopoulos2009, Hyndman2011,WicEtAl2019}. However, our motivation in this study is twofold.  First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts. In contrast to previous studies we consider individual periods rather than computing averages over a rolling window.  Second, we demonstrate how the bias correction methods discussed in the previous section along with the projection-based reconciliation help to improve forecast accuracy.

@@

	We consider ``overnight trips'' across Australia as a measure of domestic tourism flows. The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers. Hence, there are $110$ series across the hierarchy with $75$ bottom-level series. More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix. The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.

Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the aggregate overnight trips. As is usual with tourism data, these show a strong seasonal pattern with peaks observed every January corresponding to the summer vacation season in Australia. There are also some lower peaks observed in April, July and October corresponding to school term breaks. On the other hand the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation. The time plot also shows a pronounced upward trend starting from around 2010 till the end of the sample, with flows being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.

The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the geographical hierarchy. The panels below show some selected series from the second-level zones and the bottom-level regions. The plots display the diversity of time series features, within but also between levels. For example, noticeable at the first-level is the asynchronous seasonal pattern between the Northern Territory and the other states. For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February. This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season. Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being much noisier compared to the series from levels above. This of course highlights the importance of modelling series at all levels without any loss of valuable information. We should note here that we observed an anomalous (extremely high) observation for `Adelaide Hills' for December-2002. We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.

@@

    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling and MinT using a shrinkage estimator for ${\bm W}$. Squared forecast errors are computed for each series and aggregated across the whole hierarchy, i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.  We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate. We also include bottom-up forecasts in this comparison for completeness.

    The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window. We only present the results for $h=1$ but the story is identical for the other longer forecast horizons.

    As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts. The entire boxplot for OLS reconciliation is above zero.  This is not the case for WLS and MinT which for some windows generate forecasts less accurate than the base forecasts.

    The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.  Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest. The average MSE across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.

\begin{figure}[H]
    	\centering
    	\small
    	\includegraphics[width = \textwidth]{Figs/BoxPlot.pdf}
    	\caption{MSE differences between base forecasts and reconciled forecasts using OLS, MinT and WLS, and also the bottom-up approach for $h = 1$. A positive value indicates that the coherent forecasts are an improvement over the base forecasts. }\label{fig:BaseVSRecon_Fc}
\end{figure}

\begin{table}[H]
	\caption {Average {MSE($\times 10^3$)} across the whole hierarchy and over all 140 replications for h=1.}
	\label{tab:AveraveDifferences}
	\centering \tabcolsep=0.4cm
		\begin{tabular}{lccccc}
	\toprule
            & Base & OLS & MinT & WLS & Bottom-up \\
     MSE    & 4.31 & 4.20 & 4.16 & 4.48 & 5.28 \\
    \bottomrule
    \end{tabular}
\end{table}
